### 2014-03-31 paper/introduction.tex

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/teaser.png}
\caption{A novel neon sign (a) and a touch-sensitive brain (b) designed with our pipe tool and fabricated on a consumer-grade 3D printer.  (c) and (d) show the structure of the internal pipes generated by our tool.}
\label{fig:teaser}
\end{figure}

@@

\tovi{Im not sure this emphasis on
redirection/centralization is
that important (probably
does require this entire
paragraph)}
The use of pipes can allow for \emph{redirection} and \emph{centralization} of active components to various locations on a printed object's surface.   For example, to create a touch-sensitive toy as in Figure \ref{fig:teaser}, a maker can select several locations of interest on the brain.  After creating pipes to those locations and printing her object, she can fill the pipes with conductive paint.  For sensing, she need only connect a single wire to a shared out of all the tubes, and can distinguish them via Swept Frequency Capacitve Sensing \cite{Sato-touche}.  In this way, she has only a single active element (the microcontroller setup), but her otherwise-inert 3D printed object (the brain) has several active sensing locations.  This can also be used for rapid iteration of designs.  Our maker need only add a digital tube, reprint her brain, and re-fill it with copper paint to have a new version; no complicated electromechanical assembly required.

@@

Many existing sensing and actuation approaches, such as FlyEye \cite{Wimmer-flyeye}, Jamming User Interfaces \cite{Follmer-jamming}, and Touch\'{e} \cite{Sato-touche}, can be enhanced by the use of pipes.  Pipes allow makers utilizing these sensing and actuation strategies to locate input and output at arbitrary points on an object's surface.  Thus, we leverage these existing techniques for sensing and actuation while our work's novelty is in \emph{internal modeling} for 3D printing and the \emph{redirection} of IO to arbitrary locations on a device.

@@

\begin{itemize}
\item We lay out a design space of pipes and their openings, contained media, topologies, and design focus.
\item We offer algorithms and techniques for routing pipes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\item We describe the interaction possibilities of pipes, including prior work as well as uncharted possibilities.
\end{itemize}

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/teaser.png}
\caption{A novel neon sign (a) and a touch-sensitive brain (b) designed with our pipe tool and fabricated on a consumer-grade 3D printer.  (c) and (d) show the structure of the internal pipes generated by our tool.  \bjoern{will this be the robot or the UIST sign?}}
\label{fig:teaser}
\end{figure}

@@

\tovi{Im not sure this emphasis on
redirection/centralization is
that important (probably
does require this entire
paragraph)}
\bjoern{Maybe focus on this on expanding the utile and applicability of sensing techniques recently introduced in hci into types of objects not initially intended for.}
The use of pipes can allow for \emph{redirection} and \emph{centralization} of active components to various locations on a printed object's surface.   For example, to create a touch-sensitive toy as in Figure \ref{fig:teaser}, a maker can select several locations of interest on the brain.  After creating pipes to those locations and printing her object, she can fill the pipes with conductive paint.  For sensing, she need only connect a single wire to a shared out of all the tubes, and can distinguish them via Swept Frequency Capacitve Sensing \cite{Sato-touche}.  In this way, she has only a single active element (the microcontroller setup), but her otherwise-inert 3D printed object (the brain) has several active sensing locations.

@@

\bjoern{A bit repetitive with col 2 of page 1. There's opportunity for consolidation and shortening.}
Many existing sensing and actuation approaches, such as FlyEye \cite{Wimmer-flyeye}, Jamming User Interfaces \cite{Follmer-jamming}, and Touch\'{e} \cite{Sato-touche}, can be enhanced by the use of pipes.  Pipes allow makers utilizing these sensing and actuation strategies to locate input and output at arbitrary points on an object's surface.  Thus, we leverage these existing techniques for sensing and actuation while our work's novelty is in \emph{internal modeling} for 3D printing and the \emph{redirection} of IO to arbitrary locations on a device.

@@

\begin{itemize}
\item We lay out a design space of pipes and their openings, contained media, topologies, and design focus.
\item We offer algorithms and techniques for routing pipes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\item We describe the interaction possibilities of pipes, including prior work as well as uncharted possibilities. \bjoern{This last point sounds a t like the first.}
\end{itemize}
